### 2018-07-17 paper/system-model.tex
Fixes #47: Adds ref to CLOnionRouting

\name provides private and fully decentralized file sharing service by exploiting 
%% is a distributed system made of
users' devices. 
We assume any two devices can communicate with one another as soon as one knows the address of the other (\eg using the Internet, \changeFT{possibly extended with NAT traversal techniques}). The devices owned by the same user (this user's \squad) know of each other.
%Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
% the \squad they belong to.
We also assume that users can exchange some limited amounts of data 
out-of-band, \ie through some other channel than the network just mentioned (\eg 
using \ac{NFC} or QR codes).

@@

Friendly surveillance can be mitigated by ensuring security properties typically associated with onion routing \cite{[Camenisch and Lysianskaya]}{}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{} define security properties for onion
% routing:
correctness, integrity, security (wrap resistance,
indistinguishability). These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
device-unlinkability from the \ac{P2P} requirements, meaning that
using \name does not reveal the \squad a device belongs to nor the
owner and can thus not infer anything about a user's behavior such as
being online.

>>>>

\name provides a private and fully decentralized file sharing service by exploiting 
%% is a distributed system made of
users' devices. 
We assume any two devices can communicate with one another as soon as one knows the address of the other (\eg using the Internet, \changeFT{possibly extended with NAT traversal techniques}). The devices owned by the same user (this user's \squad) know of each other.
%Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
% the \squad they belong to.
We also assume that users can exchange some limited amounts of data 
out-of-band, \ie through some other channel than the network just mentioned (\eg 
using \ac{NFC} or QR codes).

@@

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing \cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
correctness, integrity, security (wrap resistance,
indistinguishability). These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
device-unlinkability from the \ac{P2P} requirements, meaning that
using \name does not reveal the \squad a device belongs to nor the
owner and can thus not infer anything about a user's behavior such as
being online.
